---
title: "CARS response dashboard"
output: 
  html_document: 
    css: "style.css"
---
```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri("./af-logo.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:60px;')
```

```{r echo=FALSE, warning=FALSE}

library(magrittr)


data <- get_tidy_data_api()
department <- filter_divisons(data)
n_responses <- length(department)

department_table <- data.frame(table(remove_low_counts(department)))

```

## Welcome

Welcome to the Coding in Analysis and Research Survey (CARS) 2026 dashboard. Here you can see the response rate by department.  

CARS is our annual survey on the use of code in government analysis. You can see the previous results in our [online publication](https://best-practice-and-impact.github.io/CARS/). 

This year we hope to get over 1,500 responses. So far, we've got `r n_responses` responses. We will create a customised report for departments where we receive over 20 responses. If you're interested in seeing this, please promote the survey in your department.


## Responses by department

```{r echo=FALSE, warnings=FALSE}

if (nrow(department_table) == 0) {
  knitr::raw_html("There aren't enough responses yet. Please check back later.")
} else {
  colnames(department_table) <- c("Department", "Number of respondents")

  plot <- plot_freqs(department_table, xlab = "Department", ylab = "Number of respondents", n = n_responses, font_size = 14, height = 400 + 50 * nrow(department_table), width = 800)
  
  table <- kableExtra::kable_styling(knitr::kable(department_table)) %>% 
    kableExtra::add_footnote(paste0("Sample size = ",n_responses)) 
  
  CARS::wrap_outputs("coding-freq", plot, table)
}

```

## Can't see your department?

If your department isn't listed here, that means we have fewer than 5 responses. Once we get to that number of responses, you'll be able to see it listed.